\Title

### 2020-12-10 manuscript/manuscript.tex
Include section comparing with boostrap inversion

SOMETHING ABOUT THE VON FRESE 88 PAPER (BOOTSTRAP INVERSION) AND HOW THIS IS
DIFFERENT.

>>>>

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are:
(1) the sources in the overlapping portions of the windows are fit more than
once, allowing the algorithm to self-correct for poor solutions to any given
window;
(2) using only data points within the window when fitting the data enables the
use of larger datasets;
(3) experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.
